%@@@@% !TEX root = ../resume.tex
\cvsection{Professional Experience}
\begin{cventries}
   \cventry
     {Raytheon Missiles and Defense}
     {Mid-Level Simulation and Modeling Engineer}
     {Tucson, AZ}
     {May 2020 - Present}
     {
       \begin{cvitems}
       \item{\textbf{Active Secret Clearance}}
        \item{Recognized SME within program on C++, CUDA, Git, and Grid-based Massively Parallel Computing.}
        \item{Specialized in optimization of FPGA and Signal Processing Algorithms.}
        \item{Led year long study into optimization of a Monte Carlo simulation, resulting in over 80\% reduction in regression runtime. Program-wide development loop tightened from days to hours.}
        \item{Frequently collaborated across teams to support detection algorithm design.}
        \item{Supported company onboarding process by acting as a new hire ambassador.}
        \item{Demonstrated proficiency in analysis, diagnosis, and subsequent treatment of simulation defects that had eroded compliance.}
        \item{Development was primarily conducted in C++, but non-trivial work was also completed in Fortran 77/95, Perl, Python, and Matlab.}
       \end{cvitems}
     }
   \cventry
     {Martin Defense Group (Formerly Navatek Ltd.)}
     {Naval Engineering Intern}
     {Kingston, RI}
     {May 2019 - Aug. 2019}
     {
       \begin{cvitems}
        \item{Designed and Implemented a framework for Augmented Reality Registration using fiducial markers in C++.}
        \item{Presented work weekly to project stakeholders in Department of the Navy to ensure compliance with customer requests.}
        \item{Coordinated with team members to integrate Pose Estimation to achieve centimeter-level precision.}
       \end{cvitems}
     }
  \cventry
    {Smart Networking and Computing (SNeC) Lab}
    {Graduate Research Assistant, Undergraduate Lab Coordinator}
    {Kingston, RI}
    {May 2018 - May 2020}
    {
      \begin{cvitems} 
        \item{Developed novel algorithm that minimizes energy usage and latency of mobile-based deep learning inference using real-time task partioning.}
        \item{Developed system for Augmented Reality aided health management in collaboration with Rhode Island Veterans Affairs.}
        \item{Developed Augmented Reality application to improve driver awareness using existing "dashcam" hardware.} 
        \item{Led team of four engineers on development of cyclist gear designed to increase visibility to self-driving automotive systems.}
      \end{cvitems}
    }
    
  \cventry
    {Hand-held Arbitrary Waveform Generator - AstroNova Inc.}
    {Embedded Systems Engineer}
    {Kingston, RI}
    {Aug. 2017 - May 2018}
    {
      \begin{cvitems}
        \item {Designed and implemented FPGA-based architecture using VHDL and Xilinx Vivado Tools.}
        \item {Wrote firmware to support control of waveform parameters using C and Vivado SDK.}
        \item {Assisted in writing PC based application for fine control of waveforms using C\#.}
      \end{cvitems}
    }
  %\cventry
  %  {IT Hardware Specialist}
  %  {University of Rhode Island IT Services}
  %  {Kingston, RI}
  %  {Oct. 2016 - May 2018}
  %  {
  %    \begin{cvitems}
  %      \item {Serviced/optimized hardware and software daily for students/faculty. Honed communication and teamwork skills.}
  %    \end{cvitems}
  %  }
  %\cventry
  %  {Production Engineering Intern}
  %  {VoltServer Inc.}
  %  {East Greenwich, RI}
  %  {Mar. 2017 - Aug. 2017}
  %  {
  %    \begin{cvitems}
  %      \item {Designed and constructed production testing / validation equipment and software.}
  %      \item {Performed RMA work on high voltage power transmission boards. Honed soldering ability.}
  %    \end{cvitems}
  %  }
 \end{cventries}
